\documentclass[a4paper,11pt]{article}
\usepackage{amsmath, amsfonts, amssymb}
\usepackage[english, russian]{babel}
\textheight = 230mm \textwidth = 160mm \topmargin = -2mm
\oddsidemargin=6mm \evensidemargin=6mm \makeindex
\begin{document}
\large
\makeatletter
\renewcommand{\@evenhead}{\vbox{\thepage\hfil{\verb "—арымсаковские чтени€, “ашкент-2021"}\hrule}}
\renewcommand{\@oddhead}{\vbox{\hfill{\verb "—арымсаковские чтени€, “ашкент-2021"}
\hfill\thepage\hrule}} \makeatother
\begin{center}
\textbf{CARLEMAN'S FORMULA OF A SOLUTIONS OF THE POISSON
EQUATION IN BOUNDED DOMAIN} \\
\medskip
\textbf{Sattorov E.\, N. $^{1}$, Ermamatova  Z.\,E.$^{2}$} \\
\smallskip
{Samarkand State University , Samarkand, Uzbekistan,}\\
{e-mail1@Sattorov-e@rambler.ru;}\\
{Samarkand State University , Samarkand, Uzbekistan,}\\
{e-mail2@zuxroermamatova@rambler.ru}
\end{center}

Poisson equation or potential equation [1]
$$
 -\triangle U(x)\equiv -\sum\limits_{i=1}^{3}\frac{\partial^2 U}{\partial x_i^2} =f(x), \eqno(1)
$$
is the classical example for second order elliptic partial
differential equations and it is a mathematical model to some
important physical phenomena. It has applications in many different
areas such as plasma physic, electrocardiography, and corrosion
non-destructive evaluation (e.g., [2], [3],[4], [5], [6]).

In this paper, we offer an explicit formula for reconstruction of a
solution of the Poisson equation in bounded domain from its values
and the values of its normal derivative on part of the boundary,
i.e., we give an explicit continuation formula for a solution to the
Cauchy problem for the Poisson equation.

Let $R^3$ is the third dimensional real Euclidean space,
$$x=(x_1,x_2,x_3),\,\ y=(y_1,y_2,y_3)\in R^3, \,\ x'=(x_1,x_2),
\ y'=(y_1,y_2)\in  R^2,$$$$ s=\alpha
^2=|y'-x'|=(y_1-x_1)^2+(y_2-x_2)^2,\,\ r^2=s+(y_3-x_3)^2=|y-x|^2,
\tau=tg\frac{\pi}{2\rho},\,\ \rho>1,\,\
$$$$G_\rho=\{y:|y'|<\tau y_3,\,\ y_3>0\},\,\ \partial
G_\rho=\{y:|y'|=\tau y_3,\,\ y_3>0\}, \,\
\overline{G}_\rho=G_\rho\cup\partial G_\rho,\,\
\varepsilon,\varepsilon_1
$$
and $\varepsilon_2$ sufficiently small positive constants,
$$G_\rho^\varepsilon=\{y:|y'|<\tau(y_3-\varepsilon)\},\,\
\partial G_\rho^\varepsilon=\{y:|y'|=\tau(y_3-\varepsilon)\}
\,\ \overline{G}_\rho^\varepsilon=G_\rho^\varepsilon\cup
\partial G_\rho^\varepsilon,$$
$$
C=\{\varsigma:\varsigma=\xi+i\eta,\,\ -\infty<\xi<\infty, \,\
-\infty<\eta<\infty,\} .
$$
$\Omega_\rho-$ is a bounded simply connected domain whose boundary
in $R^3$  whose boundary $\partial\Omega_\rho$ consists of a part of
the conic surface $T\equiv\partial G_\rho$ and a smooth surface $S,$
lying inside the cone $\overline{G}_\rho.$ The case $\rho=1$ is the
limit case. In this case $G_1 $ is the half-space $y_3>0,\partial
G_1 $ is the hyperplane $y_3=0,$ and $\Omega_1$ is a bounded simply
connected domain whose boundary consists of a compact connected part
of the hyperplane $y_3=0$ and a smooth surface $S$ in the half-space
$y_1\geq 0,\,\ \overline{\Omega}_\rho=\Omega_\rho\cup\partial
\Omega_\rho,\,\ S_0,$ is the interior of $S,$ and function $f$
H\"{o}lder continuous with exponent $\lambda \in (0,1), $ i.e., $f
\in C^{s,\lambda}(\overline{\Omega}_\rho)$ and $s\in Z_+.$

\textbf{Problem.}  Let we know the Cauchy data for a solution to
system (0.1) on the surface $S$:

$$U(y) = f_1(y), \frac{\partial U(y)}{\partial n} =f_2(y), y\in S  \eqno(2) $$
where $n = (n_1, n_2, n_3)$ is the unit outward-pointing normal to
the surface $\partial \Omega$ at a point $y$, and $f_1 , f_2 $ are
continuous vector-functions. Given $f_1(y)$ and $f_2(y)$ on $S$,
find $U(x)$  $x\in \Omega$.

The Cauchy problem (2)for the Poisson equation (1) is well-known to
be ill-posed [7], [8].  Hadamard [9] noted that solution to problem
is not stable. Possibility of introducing a positive parameter
$\sigma$, depending on the accuracy of the initial data, was noticed
by M. M. Lavrent'ev [10]. Uniqueness of the solution follows from
the general theorem by Holmgren [11].  Traditionally, regularization
techniques, such as Tikhonov regularization [12].

We suppose that a solution to the problem exists (in this event it
is unique) and continuously differentiable in the closed domain and
the Cauchy data are given exactly. In this case we establish an
explicit continuation formula. This formula enables us to state a
simple and convenient criterion for solvability of the Cauchy
problem.

The result established here is a multidimensional analog of the
theorems and Carleman-type formulas [13], by G.M.Goluzin,
V.I.Krylov, V.A.Fok, and F.M.Kuni in the theory of holomorphic
functions of one variable [14],[15].

\begin{center}
\textsl{REFERENCES}
\end{center}
1. Gilbarg D., Trudinger N. Elliptic partial differential equations
of second order, Springer-Verlag Berlin Heidelberg, New
York, Tokyo 1983 \\
2. Blum J., Numerical simulation and optimal control in plasma
physics, New York, NY; John Wiley and Sons Inc., 1989.\\
3. Chen G. and Zhou J. , Boundary Element Methods, Academic Press,
London, 1992.\\
4. Colli-Franzone P., Guerri L., Tentoni L., Viganotti L., Baruffi
S., Spaggiari S., and Taccardi B., A mathematical procedure for
solving the inverse potential problem of electrocardiography.
Analysis of the time-space accuracy from in vitro experimental data,
Mathematical Biosciences, 77 (1985), pp. 353-396.\\
5. Fasino D. and Inglese G., An inverse Robin problem for Laplace's
equation: theoretical results and numerical methods,
Inverse problems, 15 (1999), p. 41.\\
6. Inglese G., An inverse problem in corrosion detection, Inverse
problems, 13 (1997), p. 977.\\
7. Alessandrini G., Rondi L., Rosset E., and  Vessella S., The
stability for the Cauchy problem for elliptic equations, Inverse
problems, 25 (2009), p. 123004.\\
8. Belgacem F. B., Why is the Cauchy problem severely ill-posed?,
Inverse Problems, 23 (2007), p. 823.\\
9. Hadamard J., Lectures on the Cauchy Problem in Linear Partial
Differential Equations, Yale University Press, New Haven, 1923.\\
10. Lavrentev, M. M. Some Improperly Posed Problems in
Mathematical Physics (Springer, Berlin, 1967).\\
11. Bers, L., John, F., Schechter, M. Partial Differential
Equations (Interscience, New York, 1964).\\
12. Tikhonov A. N. and Arsenin V. Y., Solutions of ill-posed
problems, Winston, 1977.\\
13. Arbuzov, E. V., Bukhgeim, A. L. УThe Carleman Formula for the
MaxwellТs Equations on a PlaneФ, Sib. Elektron. Mat. Izv., No. 5,
448-455 (2008) [in Russian].\\
14. Goluzin G. M. and Krylov V.I., "A generalized Carleman fornula
and its application to analytic continuation of functions,"Vat.Sb.,
40, No.2, (1933), p.144-149 . \\
15. Fok V.A. and Kuni F.M., "On the introduction of a 'suppressing'
function in dispersion relations," Dokl. Akad. Nauk SSSR, 127, No.
6, (1959), p. 1195-1198. \\

\end{document}
